Quality measure notes

### 2021-07-14 StateOfPractice/Ao-Report/12Background.tex
ao report - minor updates

When designing a method for evaluating the state of the practice of domain-specific software, we included a step to select domain and software. Knowledge of different software categories is essential for the selections. To compare and grade the software qualities with the grading template in Appendix \ref{ap_grading_template}, we need the definitions of qualities and the Analytic Hierarchy Process (AHP).

@@

\subsection{Freeware}
\label{sec_freeware}
Freeware is software that can be used free of charge. Unlike with OSS, the authors of freeware typically do not allow users to access or modify the source code of the software \cite{LINFO2006}. The term \textit{freeware} should not be confused with \textit{free software}, which is similar to OSS but with a few differences. To the end-users, the differences between freeware and OSS often do not bother them. The fact that these products are free of charge is likely to make them popular with many users. However, software developers, end-users who wish to modify the source code, and researchers looking for inner characteristics may find the inaccessible source code to be a problem.

>>>>

When designing a method for evaluating the state of the practice of domain-specific software, we included a step to select domain and software. Knowledge of different software categories is essential for the selection. To compare and grade the software qualities with the grading template in Appendix \ref{ap_grading_template}, we need the definitions of qualities and the Analytic Hierarchy Process (AHP).

@@

\subsection{Freeware}
\label{sec_freeware}
Freeware is software that can be used free of charge. Unlike with OSS, the authors of freeware typically do not allow users to access or modify the source code of the software \cite{LINFO2006}. The term \textit{freeware} should not be confused with \textit{free software}, which is similar to OSS but with a few differences. To the end-users, the differences between freeware and OSS often do not bother them. The fact that these products are free of charge is likely to make them popular with many users. However, software developers, end-users who wish to modify the source code, and researchers looking for inner characteristics may find the inaccessible source code a problem.
